Bird beak's elaboration and innovation

### 2022-07-14 Analysis/04-Figure3_with_ellipse_scalling_and_8D_histograms.Rmd
Added mushed ellipses

```{r, eval = TRUE, echo = FALSE}
box_size <- 1.5
pdf(file = "../Manuscript/Figures/Figure3_ellipses.pdf", height = box_size*8, width = box_size*10)

@@

## Global window parameters
lay_mat_order <- rbind(
        matrix(c(1,1, 2:9), ncol = 10, nrow = 1), # line 1
        matrix(c(1,1, 10:17), ncol = 10, nrow = 1), # line 2
        matrix(c(1,1, 18:25), ncol = 10, nrow = 1), # line 3
        matrix(c(26:35), ncol = 10, nrow = 1), # line 4
        matrix(c(36:45), ncol = 10, nrow = 1), # line 5
        matrix(c(46:55), ncol = 10, nrow = 1) # line 6
    )
lay_mat_super <- rbind(
        matrix(c(1,1, 2:9), ncol = 10, nrow = 1), # line 7
        matrix(c(1,1, 10:17), ncol = 10, nrow = 1) # line 8
    )
heights_vals <- rep(1, 9)
widths_vals <- rep(c(1, 1/3), 5)
layout_matrix <- layout(rbind(lay_mat_super, (lay_mat_order+17)), widths = widths_vals, heights = heights_vals, respect = TRUE)

@@

## Plotting the ellipses
for(i in 1:length(tip_order)) {
    ## Plot each pannel
    wrap.plot.ellipses(i, tip_colours_orders, order_shapespace, results$order_results_between)
}
dev.off()

>>>>

```{r, eval = TRUE, echo = FALSE}
box_size <- 1.5
pdf(file = "../Manuscript/Figures/Figure3_ellipses_2.pdf", height = box_size*8, width = box_size*10)

@@

## Global window parameters
lay_mat_order <- rbind(
        matrix(c(1,1, 2:9), ncol = 10, nrow = 1), # line 1
        matrix(c(1,1, 10:17), ncol = 10, nrow = 1), # line 2
        matrix(c(57,58, 18:25), ncol = 10, nrow = 1), # line 3
        matrix(c(26:35), ncol = 10, nrow = 1), # line 4
        matrix(c(36:45), ncol = 10, nrow = 1), # line 5
        matrix(c(46:55), ncol = 10, nrow = 1) # line 6
    )
lay_mat_super <- rbind(
        matrix(c(1,1, 2:9), ncol = 10, nrow = 1), # line 7
        matrix(c(73,0, 10:17), ncol = 10, nrow = 1) # line 8
    )
heights_vals <- rep(1, 9)
widths_vals <- rep(c(1, 1/3), 5)
layout_matrix <- layout(rbind(lay_mat_super, (lay_mat_order+17)), widths = widths_vals, heights = heights_vals, respect = TRUE)

@@

## Plotting the ellipses
for(i in 1:length(tip_order)) {
    ## Plot each pannel
    wrap.plot.ellipses(i, tip_colours_orders, order_shapespace, results$order_results_between)
}

## Plotting the aligned and scale ellipses for the superorders
par(bty = "n")
lims <- c(-1/3, 1/3) # c(-1.25, 1.25)
plot(NULL, xlim = lims, ylim = lims, xaxt = "n", yaxt = "n", xlab = "n", ylab = "n")
abline(v = 0, col = "grey", lwd = 0.5)
abline(h = 0, col = "grey", lwd = 0.5)
covar.plot(superorder_shapespace, ellipses = mean,
           col = match.col(superorder_shapespace, tip_colours_super_orders),
           legend = FALSE, points = FALSE, scale = "phylogeny",
           lines.lwd = c(rep(1, length(tip_colours_super_orders)), 3),
           add = TRUE, n = 50)

load("../Data/Processed/tip_colours_orders.rda")
par(bty = "n")
lims <- c(-1/3, 1/3) # c(-1.25, 1.25)
plot(NULL, xlim = lims, ylim = lims, xaxt = "n", yaxt = "n", xlab = "n", ylab = "n")
abline(v = 0, col = "grey", lwd = 0.5)
abline(h = 0, col = "grey", lwd = 0.5)
covar.plot(order_shapespace, ellipses = mean,
           col = match.col(order_shapespace, tip_colours_orders),
           legend = FALSE, points = FALSE, scale = "phylogeny",
           lines.lwd = c(rep(0.5, length(tip_colours_orders)), 3),
           add = TRUE, n =50)

dev.off()
